% CV template
%
% Author: Christopher Keyes
% Updated: September 24, 2021
%
% OK to use and edit!

\documentclass{cv_style}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{amsmath}
\usepackage[colorlinks = true, linkcolor = blue, urlcolor = blue, citecolor = blue, anchorcolor = blue]{hyperref}

\begin{document}

	\footnotetext[1]{Updated \today}
    \pagenumbering{gobble}

    \begin{center} \name{Ian Jorquera} 

    \contact{Colorado State University}{Department of Mathematics}{Weber 223}{\href{mailto:jorquera@colostate.edu}{jorquera@colostate.edu}}{\href{https://jorqueraian.github.io/}{Website}}
    
	\end{center}
	
	\section{Academic Interests}
	Frame Theory, Structure of frames over finite fields, Category Theory and applications, Algorithm Design, Functional Programming, Complexity Theory

	\section{Education}
		\subsection{Colorado State University}
				\begin{itemize}
					\item Ph.D., Mathematics, Gem Fellow, (expected graduation: 2027).
					\item Advisor: Emily J. King
				\end{itemize}

		\subsection{Colorado State University}
				\begin{itemize}
					\item Masters, Mathematics, Gem Fellow, (expected graduation: 2025).
					\item Advisor: Emily J. King
				\end{itemize}
				
		\subsection{University of Colorado Boulder}
				\begin{itemize}
					\item B.A., Computer Science, \textit{Summa Cum Laude} (2022).
					\item B.A., Mathematics, \textit{with Honors} (2022).
					\item Minor, Applied Mathematics (2022)
				\end{itemize}
	
	\section{Positions}
		\subsection{Current}
				\subsubsection*{Colorado State University}
					\begin{itemize}
						\item GEM Fellow, Graduate Teaching Assistant. 8/2022 - present
					\end{itemize}
				
		\subsection{Previous}
			\subsubsection*{Oak Ridge National Laboratory}
				\begin{itemize}
					\item GEM Fellow, Research Intern, Programming Systems Group. 6/2022-8/2022
					\item Advisor: Pedro Valero{-}Lara
				\end{itemize}
		
% \paper[Collaborator's name]{Title}{Status (e.g.\ in prep., submitted, accepted)}{(links)}

	\section{Publications and Preprints}
		\begin{etaremune}			
					\item \paper[William F. Godoy and
					Pedro Valero{-}Lara and
					T. Elise Dettling and
					Christian Trefftz and
					Thomas Sheehy and
					Ross G. Miller and
					Marc Gonz{\'{a}}lez Tallada and
					Jeffrey S. Vetter and
					Valentin Churavy]{Evaluating performance and portability of high-level 
					programming models: Julia, Python/Numba, and Kokkos on exascale nodes (2023)}
					{accepted}{(https://doi.org/10.1109/IPDPSW59300.2023.00068)}
					\item \paper[Pedro Valero{-}Lara and
					Frank Liu and
					Jeffrey S. Vetter]{Mixed-Precision {S/DGEMM} Using the {TF32} and {TF64} Frameworks on
					Low-Precision {AI} Tensor Cores(2023)}{accepted}{(https://doi.org/10.1145/3624062.3624084)}
					%\item \paper[Names]{Title}{Status}{(links)}
					
		\end{etaremune}
		
% \talk{title}{venue}{host}{date}
		
	%\section{Invited Conferences}
	%	\begin{etaremune}
	%		\item \talk{Talk title}{Venue or location}{Host organization}{Date}
	%	\end{etaremune}
		
	\section{Attended Conference}
		\begin{etaremune}
			\item Recent Progress on Optimal Point Distributions and Related Fields, ICERM, Brown University, June 2024. Funded by Conference.
			\item Groups, Nilpotence, and Tensors, Colorado State University, April 2023.
		\end{etaremune}

		\section{Seminar Talks}
		\begin{etaremune}
			\item \talk{What is Algebra? Why should you care? And what make it so abstract anyways?}{Colorado State University}{Greenslopes Mathematics and Statistics Seminar}{October 2024}
			\item \talk{Composition, Categories, and Databases}{Colorado State University}{Applied Category Theory Seminar}{September 2024}
			\item \talk{Suboject Classifiers and Defining a Topos}{Colorado State University}{Applied Category Theory Seminar}{April 2024}
			\item \talk{F-Algebras and Catamorphisms in Scala}{Colorado State University}{Applied Category Theory Seminar}{November 2023}
			\item \talk{Simple Types}{Colorado State University}{Applied Category Theory Seminar}{January 2023}
			\item \talk{The DisCoCat (Distributional Compositional Categorical) model of meaning}{Colorado State University}{Applied Category Theory Seminar}{October 2022}
			\item \talk{Examples of Functors and Natural Transformations}{Colorado State University}{Applied Category Theory Seminar}{September 2022}
		\end{etaremune}

		\section{Seminars Organized}
		\begin{etaremune}
			\item \talk{Greenslopes Graduate Seminar}{Co-Organizer}{Colorado State University}{August 2024 - Decmber 2024}
		\end{etaremune}
		
	\section{Teaching Experience}
	\subsection{Colorado State University}
	\begin{itemize}
		\item Instructor, Math 160 (Spring 2025).
		\item Assistant Coordinator, Math 160 (Fall 2024).
		\item Assistant Coordinator, Math 160 (Spring 2024).
		\item Instructor, Math 160 (Fall 2023).
		\item Teaching Assistant, Math 369 (Summer 2023).
		\item Teaching Assistant, Math 155 (Spring 2023).
		\item Instructor, Math 160 (Fall 2022).
	\end{itemize}
	\subsection{University of Colorado Boulder}
		\begin{itemize}
			\item Undergraduate Course Assistant, CSCI 3104
		\end{itemize}
		
	%\section{Organizations}
	
	%\subsection{Seminars}
	%\begin{itemize}
	%	\item Co-organizer of \textit{Seminar title}, with Collaborator Name(s) (semesters). Seminar \href{https://seminarwebsite.com}{website}.
	%\end{itemize}
	
	%\subsection{Professional society chapter}
	%Do you run your school's professional society? If so, list that here.
		
	\section{Outreach}
		\begin{itemize}
			\item Volunteer, CSU Math Day (November 2024).
			\item Volunteer, CSU Math Day (November 2023).
		\end{itemize}
		
	\section{Awards}
		\begin{itemize}
			\item GEM PhD Fellow, Sponsored by Oak Ridge National Laboratory and Colorado State University (2022).
		\end{itemize}

\end{document}
