\documentclass[12pt]{amsart}
\usepackage{preamble}

\begin{document}
\begin{center}
    \textsc{Math 517. HW 2\\ Ian Jorquera}
\end{center}
\vspace{1em}

\begin{itemize}
    \item[1.] Let $\sum_{k=1}^{\infty}{a_k}$ be a conditionally convergent series which
        converges to $L$ This also means that $\lim_{k\ra\infty}|a_k|=0$ and so for
        $\varepsilon=1$ there exists some $M$ such that $|a_k|<1$ for all $k>M$. This
        also means the subseries $\sum_{k=1}^{\infty}{a^-_k}$ and
        $\sum_{k=1}^{\infty}{a^+_k}$ both diverge. Now construct a series as follows.
        First pick $m_1$ minimally such that $\sum_{k=1}^{m_1}{a^+_k}> 1$, which we can
        do as the series diverges to $\infty$. Then pick $n_1=1$ which corresponds to
        the partial sum $\sum_{k=1}^{m_1}{a^+_k}+\sum_{k=1}^{n_1}{a^-_k}$. Repeat this
        process inductively such that $m_j$ is chosen minimally such that
        $\sum_{k=1}^{m_j}{a^+_k}+\sum_{k=1}^{n_{j}-1}{a^-_k}> j$ and $n_j=j$. This
        gives us a rearrangement $p$. Notice that the series
        $\sum_{k=1}^{\infty}{a_{pk}}$ diverges as for any $N>0$ we may pick $\ell$ such
        that the subsequence $\{a_{p1},\dots,a_{p\ell}\}$ contains all element $a_k$
        where $k\leq\max{(M, m_{N+1})}$ and then notice that
        $|\sum_{k=1}^{n}{a_{pk}}|>N$ for all $n>\ell$. If it were not then it would be
        the case that the last element added was a negative term too large but by
        construction $|a_{pk}|<1$ for all $k>\ell$ and the
        $|\sum_{k=1}^{n-1}{a_{pk}}|>N+1$ so it would have to be the case
        $|\sum_{k=1}^{n}{a_{pk}}|>N$.

    \item[2.]
        WLOG assume that $c_1<c_2$. Let $\sum_{k=1}^{\infty}{a_k}$ be a conditionally
        convergent series which converges to $L$. This also means the subseries
        $\sum_{k=1}^{\infty}{a^-_k}$ and $\sum_{k=1}^{\infty}{a^+_k}$ both diverge. Now
        construct a series as follows. First pick $m_1$ minimally such that
        $\sum_{k=1}^{m_1}{a^+_k}> c_2$, which we can do as the series
        $\sum_{k=1}^{\infty}{a^+_k}$ diverges to $\infty$. Then pick $n_1$ minimally
        such that the partial sum $\sum_{k=1}^{m_1}{a^+_k}+\sum_{k=1}^{n_1}{a^-_k}<c_1$
        which can be done because the series $\sum_{k=1}^{\infty}{a^-_k}$ diverges to
        $-\infty$. Repeat this process inductively such that $m_j$ is chosen minimally
        such that $\sum_{k=1}^{m_j}{a^+_k}+\sum_{k=1}^{n_{j-1}}{a^-_k}> c_2$ and $n_j$
        is chosen minimally such that
        $\sum_{k=1}^{m_j}{a^+_k}+\sum_{k=1}^{n_{j}}{a^-_k}< c_1$. This gives us a
        rearrangement $p$.

        Notice first that because the original series converges we know that for
        $\varepsilon>0$ there exists some $M$ such that $|a_k|<\varepsilon$ for all
        $k>M$. Now we will show that both $c_1$ and $c_2$ are cluster points in the set
        of partial sums $\{\sum_{k=1}^{n}{a_{pk}}\}_{n=1}^{\infty}$.

        Now consider the subsequence $\{\sum_{k=1}^{m_j}{a_{pk}}\}_{j=1}^{\infty}$ That
        is we are considering only the partial sums that ead at an index $m_j$ as
        constructed above. Notice that for any $\varepsilon>0$ we may pick $N$ such
        that the subsequence $\{a_{p1},\dots,a_{pN}\}$ contains all $a_k$ where $k>M$.
        Then for all $j>N$ we know that $|\sum_{k=1}^{m_j}{a_{pk}}-c_2|<\varepsilon$.
        This is the case as $m_j$ was picked such that $\sum_{k=1}^{m_j}{a_{pk}}>c_2$
        but $\sum_{k=1}^{m_j-1}{a_{pk}}<c_2$ and that $|a_{p{m_j}}|<\epsilon$.

        Now consider the subsequence $\{\sum_{k=1}^{n_j}{a_{pk}}\}_{j=1}^{\infty}$ That
        is we are considering only the partial sums that ead at an index $n_j$ as
        constructed above. Notice that for any $\varepsilon>0$ we may pick $N$ such
        that the subsequence $\{a_{p1},\dots,a_{pN}\}$ contains all $a_k$ where $k>M$.
        Then for all $j>N$ we know that $|\sum_{k=1}^{n_j}{a_{pk}}-c_1|<\varepsilon$.
        This is the case as $n_j$ was picked such that $\sum_{k=1}^{n_j}{a_{pk}}<c_1$
        but $\sum_{k=1}^{n_j-1}{a_{pk}}>c_2$ and that $|a_{p{n_j}}|<\epsilon$.

        % \partial S is the set of all boundary points
    \item[3.] \begin{enumerate}
            \item $S=\{0\}$. Notice first that $\R-0$ is open. To see this consider any $r\neq 0$ and notice that
                  there will always exists a number $\ell$ such that $r<\ell< 0$ if $r<0$ and $0>\ell>r$ if $r<0$.
                  In either case this give an open set
                  $(r-|\ell|, r+|\ell|)$ that does not contain $0$ and so is entirely
                  contained in $\R-0$. Meaning $\R-0$ is open and so $\{0\}$ is closed.
                  Notice also that $0$ is a boundary point of $S$ as for any $\epsilon>0$ we have that the open interval
                  $(-\epsilon,\epsilon)$ contains $0\in S$ and an element $r\not\in S$ where $0<r<\epsilon$.
                  So $\partial S =\{0\}=S$

            \item Let $S=[0,1)$ Notice that $0$ is not an interior point as for any $\epsilon>0$
                  the open set $(-\epsilon,\epsilon)$ will always contain negative numbers and so
                  $S$ can not be open. And also notice that $1$ is a cluster point as the
                  sequence $\{1-1/n\}_{n=1}^\infty$ has a limit of $1$. Because $1\not\in S$ we
                  know that $S$ is not closed

            \item Consider the unbounded set $S=\R-(0,1)=(-\infty,0]\cup [1,\infty)$. Notice that
                  every point $r\neq 0,1$ is an interior point of $S$, and $0$ and $1$ are the
                  only boundary points. So $\partial S$ is bounded by $2$.

                  % Formal? Idk. Need to show Sup is 0 which isnt in 
            \item Consider the function $f:\R\ra\R$ that maps $x\mapsto -1$ when $-1\leq x\leq 1$
                  and maps all other values $x\mapsto -\frac{1}{x^2}$. Notice that
                  $-1<-\frac{1}{x^2}<0$ when $|x|>1$ and so the range of $f$ is bounded by $2$
                  for all $x\in \R$. Notice also that the range has no maximum as $\frac{1}{x^2}$
                  gets arbitrarily close to $0$ for large enough $x$ but is never equal to zero.
                  That is $\sup(f(\R))=0\not\in f(\R)$.
        \end{enumerate}

    \item[4.] Recall first that compact sets in $\R$ are closed and bounded. And so the
        intersection $\bigcap_{n=1}^{\infty} K_n$ is closed as it is the intersection of closed sets. It is 
        also contained in the compact set $K_1$ and so is compact its self. Last we need to
        show that the intersection is non-empty.
        First we will show that compact sets are the finite union of disjoint closed
        intervals. To see this consider a compact set $K$ and assume that $K=\bigsqcup_{j}C_j$ has infinitely many disjoint
        closed sets that make it up. For each disjoint set $C_j$ we know there exists
        open sets $A_j$ and $B_j$ such that $C_j\cap K = A_j$, $B_j\cap K\neq \emptyset$, while
        $(A_j\cap K)\cup(B_j\cap K)= K$ and $(A_j\cap K)\cap(B_j\cap K)=\emptyset$. 
        Consider the open cover $\{A_j\}_j$ which by assumption has a finite
        subcover $\{A_{j_\ell}\}_{\ell=1}^n$. Notice that because each $A_j$ was
        constructed to contains only $C_j$ we know that $K=\bigcup_{\ell=1}^{n} C_{j_\ell}$ 
        as so $K$ is the finite union of disjoint compact sets. We may further
        assume that each disjoint $C_{j_\ell}$ is connected which means that it must be
        an interval.

        Notice that this means that in the chain of nested compact sets there must exists a
        chain of nested intervals that are non-empty as at every level of the nested
        compact sets there must be at least 1 interval that is non-empty. So by the
        nested interval theorem the intersection of these nested closed intervals must
        be non-empty, so the chain of nested compact sets must be non empty.
        % in non compact the example to show this is false is [n,\infty] for increasing n.

    \item[5.] Assume first that $K$ is compact. This means $K$ is a closed and bounded set.
        Consider any sequence $\{x_n\}_{n=1}^\infty\subseteq K$. Because $K$ is bounded we
        know that $\{x_n\}_{n=1}^\infty\subseteq K$ is bounded and so there must exist a
        convergent subsequence that converges to $x$, a cluster point of $K$. And
        because $K$ is compact $x\in K$.

        Now assume that $K$ is a set such that every infinite sequence
        $\{x_n\}_{n=1}^\infty\se K$ has a convergent subsequence with limit in $K$.
        Notice that this must mean that $K$ contains all its cluster points as any
        cluster point will have a infinite sequence converging to it. And so $K$ is
        closed.

        Assume $K$ is not bounded and notice that this means we may construct a
        sequence $\{x_n\}_{n=1}^\infty$ such that $|x_n|>n$. By our assumption there
        must exists a convergent subsequence $\{x_{n_j}\}_{j=1}^\infty\se K$ such that
        $x_{n_j}\ra L\in K$. However this is not possible as there will always be
        infinity many elements in the sequence that are larger then $L$ and only
        finitely many smaller then $L$. So every sequence $\{x_n\}_{n=1}^\infty$ must
        be bounded. Therefore $K$ is compact.

        this statement is slightly stronger as it only considers countable sequences
        rather then possible uncountable subsets

    \item[6.] let $f:D\ra\R$ be a function discontinuous at $a\in D$. That is there exists an
        $\varepsilon>0$ such that for all $\delta>0$ there is an $x\in D$ such that $|x-a|<\delta$
        but $|f(x)-f(a)|\geq \varepsilon$
        Notice that this means for every $\delta = \frac{1}{k}$ there must exists some corresponding
        $x_k\in D$ as described above.
        This gives us a sequence $\{x_k\}_{k=1}^\infty$ that converges to $a$. Notice also that for every
        $k$ by construction $|f(x_k)-f(a)|\geq \varepsilon$.

        Now let $f:D\ra\R$ be a function such that at the point $a\in D$ we have some
        $\varepsilon>0$ such that there exists a sequence $\{x_k\}_{k=1}^\infty$ that
        converges to $a$ and for every $k$ we have that $|f(x_k)-f(a)|\geq
            \varepsilon$. Notice that this means our function is discontinuous as for the
        $\varepsilon$ we can consider all $\delta>0$ and because $\{x_k\}_{k=1}^\infty$
        converges to $a$ there exists some $N$ such that $|x_k-a|<\delta$ for all $k>N$
        and by construction $|f(x_k)-f(a)|\geq \varepsilon$ for all $k>N$.

    \item[7.] (1) Let $f:(a,b)\ra\R$ be a function that is continuous on $(a,b)$.
        %Meaning for any point $r\in (a,b)$ and any $\varepsilon>0$ there exists $\delta>0$ where for any $x\in (a,b)$ such that $|x-r|<\delta$ we have that $|f(r)-f(x)|<\varepsilon$
        Let $O$ be an open set. Now consider any point $x\in f^{-1}(O)$ and we will
        show that it is an interior point. First let $y=f(x)$ which is its self an
        interior point of $O$, and so there exists some $\varepsilon>0$ such that
        $(y-\varepsilon, y+\varepsilon)\se O$. Because $f$ is continuous at $x$ and
        because $x$ is an interior point of $(a,b)$ we know that there exists
        $\delta>0$ where $(x-\delta,x+\delta)\se (a,b)$ and for any $r\in
            (x-\delta,x+\delta)$ where it is the case that $|x-r|<\delta$ we have that
        $|f(r)-f(x)|<\varepsilon$. This means that every element $r\in f^{-1}(0)$ and
        therefore the interval $(x-\delta,x+\delta)\se f^{-1}(O)$. And so the preimage
        of any open set is open.

        (2) Let $f:(a,b)\ra\R$ be a function such that for any open set $O$ we have that $f^{-1}(O)$ is open.
        We will show that $f$ is continuous on $(a,b)$. Fix some point $x\in (a,b)$ and again consider its image $y=f(x)$ and let
        $\varepsilon>0$ and consider the open interval $(y-\varepsilon, y+\varepsilon)$ and by assumption we know that
        $f^{-1}((y-\varepsilon, y+\varepsilon))$ is open and so contains an open interval around $x$ of length $2\delta>0$
        And notice that for any $r\in (a,b)$ such that $|x-r|<\delta$ we have that $f(r)\in(y-\varepsilon, y+\varepsilon)$ and so
        we have that $|f(r)-f(x)|<\varepsilon$. And so $f$ is continuous at all points $x\in(a,b)$

    \item[8.] Let $f:\R\ra \R$ be continuous and periodic. This means that there exists some $L$ such that $f(x)=f(x+L)$ for all $x$.
        Consider the subset $[0,L]$ which is compact and so the function $f$ is uniformly continuous on $[0,L]$, that is for any
        $\varepsilon>0$ there exists $\delta_1(\varepsilon)>0$ such that for $x,y\in\R$ where $|x-y|<\delta$ we have that $|f(x)-f(y)|<\varepsilon$.
        Notice also that the subset $[-L/2,L/2]$ is also compact and so the function $f$ is uniformly continuous on $[-L/2,L/2]$, that is for any
        $\varepsilon>0$ there exists $\delta_2(\varepsilon)>0$ such that for $x,y\in\R$ where $|x-y|<\delta$ we have that $|f(x)-f(y)|<\varepsilon$.
        Now consider any $\varepsilon >0$ and pick $\delta=\min(\delta_1(\varepsilon),\delta_2(\varepsilon), L/2)$ and notice that for any $x,y\in\R$ such that $|x-y|<\delta$
        we have assuming WLOG that $x<y$, that $(x,y)$ is contained in either $[nL,(n+1)L]$ or $[nL-L/2,(n+1)L-L/2]$ for some integer $n$.
        In either case we know that $(x-nL,y-nL)$ would be contained in either $[0,L]$ or $[-L/2,L/2]$ and so $|f(x)-f(y)|=|f(x-nL)-f(y-nL)|<\varepsilon$ and therefore
        $f$ is uniformly continuous.

    \item[9.] % wording? also correctness? i think first part is good. but second is mostly copy paste
        Let $f:K\ra\R$ be a function that is continuous on a set $K$. Let $O$ be an open set.
        Consider also the set $U=\bigcup_{x\in f^{-1}(O)}(x-\delta_x,x+\delta_x)$. Which by construction is open and $f^{-1}(0)\se U$ and so therefore
        $f^{-1}(0)\se U\cap K$ as $f^{-1}(0)\se K$.
        Where we pick $\delta_x$ as follows:
        Consider an point $x\in f^{-1}(O)$. First let $y=f(x)$
        which is an interior point of $O$, and so there exists some $\varepsilon>0$
        such that $(y-\varepsilon, y+\varepsilon)\se O$. Because $f$ is continuous we know that there exists $\delta_x>0$
        where for any $r\in K$ such that $|x-r|<\delta_x$ we have that $|f(r)-f(x)|<\varepsilon$. This means that every element $r\in f^{-1}(0)$
        and therefore the interval $(x-\delta_x,x+\delta_x)\cap K\se f^{-1}(O)$. And so $U\cap K= f^{-1}(O)$.

        Let $f:K\ra\R$ be a function on a set $K$ such that for any open set $O$ we
        have that $f^{-1}(0)=K\cap U$ for some open set $U$. We will show that $f$ is
        continuous on $K$. Fix some point $x\in K$ and again consider its image
        $y=f(x)$ and let $\varepsilon>0$ and consider the open interval
        $(y-\varepsilon, y+\varepsilon)$ and by assumption we know that
        $f^{-1}((y-\varepsilon, y+\varepsilon))=K\cap U$ for some open set $U$ and so
        $U$ contains an open interval around $x$ of length $2\delta>0$ And notice that
        for any $r\in K$ such that $|x-r|<\delta$ we have that $f(r)\in(y-\varepsilon,
            y+\varepsilon)$ and so we have that $|f(r)-f(x)|<\varepsilon$. And so $f$ is
        continuous at all points $x\in K$

\end{itemize}

\end{document}