\subsection{Step 2: Fumbling to a Definition}
\subsubsection{Jordan Pairs}
We are not saying Ottmar Loos Fumbled to the definitions we will present below 
(They are simply too nice and also intricate for that to be the case) but at some point to do
algebra you have to just fumble to something that looks good enough, and hopefully in retrospect you can convince yourself
why your algebra is a good one.

As mentioned above we want to create an algebra that looks at how pairs of modules interact, through a symmetric 
trilinear operator that we will think about as being our triple matrix product symmetricified.
So we need to define our two $k$-modules with our trilinear operator that goes between them

\begin{align*}\ip{\ip{V^+}}::&= 0_+ \\
                             &| \ip{V^+}+\ip{V^+} \\
                             &| -\ip{V^+} \\
                             &| \ip{k}\cdot \ip{V^+}\\ 
                             &| \{\ip{V^+}, \ip{V^-}, \ip{V^+}\}\end{align*}
\begin{align*}\ip{\ip{V^-}}::&= 0_- \\
    &| \ip{V^-}+\ip{V^-} \\
    &| -\ip{V^-} \\
    &| \ip{k}\cdot \ip{V^-} \\
    &| \{\ip{V^-}, \ip{V^+}, \ip{V^-}\}\end{align*}
 
And then we can define the grammar for the algebra of the pair of modules. This is the signature for a Jordan pair over $k$

\[\ip{\ip{\text{JP}_k}}::= \ip{V^+} | \ip{V^-}\]

Now that we know what operators we have in our world we need laws to tell us what these operators mean and how we can rewrite expressions.
First we need the laws that tell us that $V^+$ and $V^-$ are in fact $k$-modules.
And we also need the laws that tell about our triple product, that $\{-,-,-\}:V^\sigma\times V^{-\sigma}\times V^\sigma\ra V^\sigma$ is a trilinear operator and symmetric in the first and third terms. 

From these laws we can create additional operators. From the equivalence of symmetric bilinear maps and quadratic maps
we can define two quadratic map for $\sigma=\pm$ where
\[Q_\sigma(-):V^\sigma\ra \hom(V^{-\sigma},V^{\sigma})\text{ which are given by }2Q_\sigma(x)y = \{xyx\}\]
We can also create their corresponding symmetric bilinear maps (which recover the original $\{-,-,-\}$ product.)
$Q_\sigma(-,-):V^\sigma\times V^\sigma\ra \hom(V^{-\sigma},V^{\sigma})$ which are given by 
$Q_\sigma(x,z)=Q_\sigma(x+z)-Q_\sigma(x)-Q_\sigma(z)$.. %TODO make sure this actually works. I think i might have an off by 1/2 or 2.
Finally we will create the bilinear maps $D_\sigma(x,y)z=Q_\sigma(x,z)y=\{x,y,z\}$. Although these new operators are
unnecessarily they help which much of the theory of Jordan Pairs in a more concise way.
Notice that in the example in the section above we would have that $Q_\sigma(x)y=xyx$.

Now that we have our algebra with some initial laws we need to build some more laws using the formulas of $\text{JP}_k$.
These laws are created to mirror the behavior of our motivating examples.
We will build the following laws:
\begin{equation}
    \tag{JP1}
    \{x,y,Q_\sigma(x)z\}=Q_\sigma(x)\{y,x,z\}
\end{equation}
\begin{equation}
    \tag{JP2}
    \{Q_\sigma(x)y,y,z\}=\{x,Q_{-\sigma}(y)x,z\}
\end{equation}
\begin{equation}
    \tag{JP3}
    Q_{\sigma}(Q_{\sigma}(x)y)z=Q_{\sigma}(x)(Q_{-\sigma}(y)(Q_{\sigma}(x)z))
\end{equation}


Combining these laws we have the following definition of a Jordan Pair

\begin{definition}
    The pair $V=(V^+,V^-)$ is called a Jordan pair if $V\vDash_{\text{JP}_k}\mathcal{L}$ where $\mathcal{L}$ 
    are the laws outlined above. More Concisely we may say that a pair $V=(V^+,V^-)$ of $k$-modules
    along with a pair of quadratic maps $(Q_+,Q_-)$, which define the trilinear operator $\{-,-,-\}$, 
    is called a Jordan pair if JP1-JP3 hold in all scalar extensions of $V$
    \begin{equation}
        \tag{JP1}
        \{x,y,Q_\sigma(x)z\}=Q_\sigma(x)\{y,x,z\}
    \end{equation}
    \begin{equation}
        \tag{JP2}
        \{Q_\sigma(x)y,y,z\}=\{x,Q_{-\sigma}(y)x,z\}
    \end{equation}
    \begin{equation}
        \tag{JP3}
        Q_{\sigma}(Q_{\sigma}(x)y)z=Q_{\sigma}(x)(Q_{-\sigma}(y)(Q_{\sigma}(x)z))
    \end{equation}
\end{definition}
Note that we will often represent an element of a Jordan Pair as $x\in V$ without directly 
specifying which module $x$ is a member of. And in general a pair of objects signifies that 
objects may come from either of the $k$-modules.
Now that we have a definition for our algebra we can define what it means to have sub-objects, 
homomorphisms, congruences, quotients and ideals. None of the following are particularly surprising (You see what I did there? Im acting like a trained algebraist)
\begin{definition}
    A homomorphism $h:V\ra W$ of Jordan Pairs is a pair of maps $(h_+,h_-)$ such that $h_\sigma:V^\sigma\ra W^\sigma$ is a 
    $k$-module homomorphism such that the following holds
    \begin{equation}
        h_{\sigma}(\{x,y,z\})=\{h_{\sigma}(x),h_{-\sigma}(y),h_{\sigma}(z)\}
    \end{equation}
    This condition is equivalent to 
    \begin{equation}
        h_{\sigma}(Q_{\sigma}(x)y)=Q_{\sigma}(h_{\sigma}(x))h_{-\sigma}(y)
    \end{equation}
\end{definition}


\begin{definition}
    Let $h=(h_+,h_-)$ be a homomorphism of Jordan Pairs then the kernel of $h$ is the pair 
    $\ker(h)=(\{x\equiv z \pmod h | h_+(x)=h_+(z)\},\{x\equiv z \pmod h | h_-(x)=h_-(z)\})$
    More concisely we will write $\ker(h)=\{x\equiv z \pmod h | h(x)=h(z)\}\se V\times V$
\end{definition}

The kernel of a homomorphism $h:V\ra W$ is the resulting congruence on $V$ that relates elements by their outputs in the
homomorphism $h$. We know from Noether's Isomorphism theorem that the kernels of $V$ represent all the congruences on $V$.


Because of the underlying module structure of $V^\sigma$ we have the following observation for 
congruence of $V$: that $x\equiv z \Leftrightarrow x-z\equiv 0_\sigma$. 
This means that congruences of Jordan Pairs can be identified with the sub-object 
$()\{x\in V | x\equiv 0_\sigma\},\{x\in V | x\equiv 0_\sigma\})\se V$ up to univalence. 
In the context of kernels this means that
$(x,z)\in\ker(h)$ if and only if $h_\sigma(x-z)=0_\sigma$.
This means the Kernel of a homomorphism of Jordan Pairs can be identified with 
$\{x\in V | h_\sigma(x)=0_\sigma\}$.
We will call this type of sub-object an Ideal of $V$.

\begin{definition}
    $I=(I^+,I^-)$ is an ideal of $V$ if there exists a congruence $\equiv$ on $V$ 
    such that $x\equiv z$ if and only if $x-z\in I$. That is $I$ is an ideal if it 
    can be identified with some congruence on $V$. 
    In terms of kernels this means that 
    $I=(I^+,I^-)$ is an ideal of $V$ if there exists a homomorphism $h: V\ra W$ 
    such that $(x,z)\in \ker(h)$ if and only if $x-z\in I$. That is $I$ is an ideal if it 
    can be identified with the kernel of some homomorphism. 
\end{definition}
\begin{definition}
    Let $V$ be a Jordan Pair and $I$ an ideal then then quotient 
    $V/I$ is the partitions of $V$ defined by the congruence 
    corresponding to $I$. That is $V/I=(V^+/I^+,V^-/I^-)=(\{v+I^+|v\in V^+\},\{v+I^-|v\in V^-\})$
\end{definition}
We will henceforth associate congruences with their corresponding ideal, that is $\ker(h)=\{x\in V | h(x)=0_\sigma\}$.
This gives us a special case of Noethers Isomorphism theorem 
relating homomorphism, ideals and Quotients 
\begin{prop}
    Let $I\se V$ then the following are equivalent
    \begin{itemize}
    \item $I$ is an ideal of $V$
    \item $V/I$ is a Jordan Pair
    \item $h:V\ra V/I$ is a epimorphism with $\ker(h)=I$
    \end{itemize}
\end{prop}
This allows us a characterization of Ideals of Jordan pairs using the the equivalence of Ideals and Quotients being Jordan Pairs, and so we need only check the conditions needed on $I$ for $V/I$ to be a Jordan Pair.
\begin{prop}
$I\se V$ is an ideal of $V$ if and only if $Q_\sigma(I^\sigma)V^{-\sigma}+Q_\sigma(V^\sigma)I^{-\sigma}+\{V^\sigma,V^{-\sigma},I^\sigma\}\se I^\sigma$
\end{prop}
An important part of step 3, is the study of simples. As an important observation is that any Jordan Pair can be the image of some homomorphism, 
or in other words any Jordan pair can be the quotient of another Jordan Pair. So the simple Jordan Pairs are those whose quotients do not result any any new Jordan pairs
\begin{definition}
    A non-zero Jordan pair $V$ is called simple if $(0_+,0_-)$ and $V$ are its only ideals.
\end{definition}

To study our algebra it is often helpful to identify important objects in our examples, such as automorphisms, possibly including twisted automorphisms.
So we define 
$\text{aut}(V)=\{h:V\ra V| h \text{ is a isomorphims}\}\leq \text{GL}(V^+)\times \text{GL}(V^-)$.  
One important example of an automorphism of matrix modules is the transpose. However the standard transpose is not an automorphism of Jordan pairs.
This follows from the fact that $(-)^t:V^+=M_{p,q}(k)\ra V^-=M_{q,p}(k)$ and vice versa.
This however introduces the notion of an anti-homomorphism or twisted homomorphism.
\begin{definition}
    An antihomomorphism between Jordan pairs $V$ and $W$ is a homomorphism $\eta: (V^+,V^-)\ra(W^-,W^+)$, that is a pair of k-module homomorphisms $\eta_\sigma:V^\sigma\ra W^{-\sigma}$ such that
    $\eta_\sigma (Q_\sigma(x)y)=(Q_{-\sigma}(\eta_\sigma(x))\eta_{-\sigma} (y))$. We often denote $W^{\text{op}}$ to be the Jordan Pair $W^{\text{op}}=(W^-,W^+)$ with quadratic maps $(Q_-,Q_+)$.
    Furthermore a twisted automorphism $\eta$ is called an involution if $\eta_{-\sigma}\eta_\sigma$ is the identity map on $V^\sigma$.
\end{definition}
There are many important examples of involutions in Jordan pairs one being a transpose.

\subsubsection*{Jordan Algebras from Jordan Pairs}
A closely related algebra to the Jordan pair is the Jordan algebra. A jordan pair $V=(V^+,V^-)$ 
studies the interactions between two modules. Jordan algebras allow us to study each module somewhat independently (Although there is a rich study of Jordan Algebras unrelated to Jordan Pairs).
That is we can define the multiplication of the elements $x$ and $y$ in $V^\sigma$ as the triple 
product $x\circ y:=\{xvy\}$ for some fixed $v$. This creates a symmetric but not necessarily associative multiplication

\begin{definition}
    Let $V=(V^+,V^-)$ be a Jordan pair with $v\in V^-$ then $V^+$ is Jordan algebra, denoted $V^+_v$ with
    Jordan Product $x\circ y=\{xvy\}$ squaring operation 
    $x^2=Q_+(x)v=\frac{1}{2}\{xvx\}$ and quadratic $U$-operator 
    $U_x=Q_+(x)Q_-(v)$
\end{definition}
And likewise a definition for $V^-_v$ can be given through $V^{op}$. 
In Jordan algebras with a unit $1$ we have that $x^2=U_x(1)$, but this is generally rare in Jordan algebra that result from Jordan Pairs.
This construction provides a powerful connection between the study of Jordan pairs and quadratic Jordan algebras.

A homomorphism $h:V\ra W$ of Jordan Pairs induces a homomorphism $h_\sigma:V_v^\sigma\ra W^\sigma_{h_{-\sigma}(v)}$ on the 
