\documentclass[12pt]{article}

\usepackage[left=.6in, right=.6in, top=0.75in, bottom=0.75in]{geometry}
\setlength\parindent{0pt}

\usepackage{graphicx, amsmath,anonchap,tabularx, multicol,array,graphbox}
\usepackage{cancel}
\usepackage{enumitem}
\setlist{noitemsep}
\setlist{nolistsep}
\usepackage{float}
\usepackage{multicol}
 
%\usepackage{draftwatermark}
%\SetWatermarkText{DRAFT}
%\SetWatermarkScale{5}
%\SetWatermarkColor[rgb]{0.8,0.8,0.8}
\newenvironment{boxe}
    {\begin{center}
    \begin{tabular}{|p{0.9\textwidth}|}
    \hline\\
    }
    { 
    \\\\\hline
    \end{tabular} 
    \end{center}
    }
    
\begin{document}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l}
\textbf{Optimization Workshop}   \\
\end{tabular*} \\

\vspace{.1in}
\small
\textbf{Remember to:} \textit{Check the critical points AND the boundary points when you are looking for global max/min.}
\vspace{.1in}
\begin{enumerate}
    \item Consider the function $f(x)=x^3+ax$ on the interval $[-3,2]$ where $a$ is a constant.
    \begin{itemize}
        \item Find the critical points of $f(x)$ in terms of $a$.\\\\\\\\\\
        \item Will $f(x)$ always have a global maximum and minimum? How do you know?\\\\\\
        \item Is there a value for $a$ such that there will be a global maximum at $x=-2$? If so find it.\\\\\\\\\\\\\\\\\\
        \item Is there a value for $a$ such that there will be a global maximum at $x=2$? If so find it.\\\\\\\\\\\\\\\\\\\\\\
        \item T/F: There is a value for $a$ such that there is a global maximum at $x=0$. (Hint: Can $x=0$ be a critical point? When it is, can it also be a local minimum or maximum?)\\
    \end{itemize}
   % \newpage
    
    \newpage
    \item Find the area of the largest rectangle that can be inscribed in the ellipse $\displaystyle{\frac{x^2}{4}+y^2}=1$
    \begin{itemize}
        \item Draw a picture and assign variable to all important quantities. Indicate what quantity needs to be maximized and what constraints you have (Hint: Label the corners of your rectangle as points)\\\\\\\\\\\\\\\\\\\\\\

        \item Write a general equation for the quantity you are maximizing or minimizing in terms of one variable.\\\\\\\\\\

        \item Now that you have an equation. Find an interval for your input variable that makes sense for your problem. Does EVT apply? \\\\
        
        \item Find the critical points of your function.\\\\\\\\\\\\\\\\\\\\

        \item Now using the critical points find the maximum or minimum value of your function (don't forget to check the endpoints).\\\\\\\\\\

        \item Now use what you have found to answer the original questions.
    \end{itemize}
        
    
\end{enumerate}


\end{document}
