\documentclass[12pt]{article}
% We can write notes using the percent symbol!
% The first line above is to announce we are beginning a document, an article in this case, and we want the default font size to be 12pt
\usepackage[utf8]{inputenc}
% This is a package to accept utf8 input.  I normally do not use it in my documents, but it was here by default in Overleaf.
\usepackage{pgfplots}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx, amsmath,anonchap,tabularx, multicol,verbatim}
\usepackage{hyperref}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}

\usepackage{xcolor}
\usepackage{graphicx}

\usepackage{enumitem,mdwlist}
% These three packages are from the American Mathematical Society and includes all of the important symbols and operations 
\usepackage{fullpage}
% By default, an article has some vary large margins to fit the smaller page format.  This allows us to use more standard margins.

\setlength{\parskip}{1em}
% This gives us a full line break when we write a new paragraph

\newenvironment{boxe}
    {\begin{center}
    \begin{tabular}{|p{0.9\textwidth}|}
    \hline\\
    }
    { 
    \\\\\hline
    \end{tabular} 
    \end{center}
    }

\begin{document}
% Once we have all of our packages and setting announced, we need to begin our document.  You will notice that at the end of the writing there is an end document statements.  Many options use this begin and end syntax.

\begin{center}
    \Large Math 160: Choose your own Adventure: Solving limits
\end{center}

\section{Solving limits: algebraically}

You've been given a limit $\displaystyle{\lim_{x\to c}f(x)}$ (possible a one sided limit). Now how do we solve it?\\

If $c$ is a number(ex. $\lim_{x\rightarrow 2}f(x)$) go to section \ref{ssec:number}. 
If $c$ is $\pm \infty$(ex. $\lim_{x\rightarrow \infty}f(x)$) go to section \ref{ssec:inf}.\\

\subsection{Evaluating limits at a number}
\label{ssec:number}
If $f(x)$ has an absolute value sign in the function ($|\cdot|$). Rewrite it as a piece-wise function(See Example~\ref{ex:abs}).\\

If $f(x)$ is a piece-wise function, we likely need to use one-sided limits focusing on only the relevant pieces of the function for the one sided limits.

If $f(x)$ is a ``normal'' function then we can (probably) follow the steps below:

\begin{enumerate}
    \item \label{b:step1} First try directly plugging in $x=c$ to your function. 
    If you get a value, you are done! If not, you will get an indeterminate form
    If you get $\frac{k}{0}$ for some constant $k$ go to part \ref{b:kz}. If you get  $\frac{0}{0}$ go to part \ref{b:zz}.
    \begin{enumerate}[label=(\alph*)]
        \item \label{b:zz} You got the indeterminate form $\displaystyle{\lim_{x\to c}f(x)}=$``$\frac{0}{0}$''. 
        This indicates that we need to somehow cancel common terms. Try factoring or if your function has 
        a $\sqrt{\cdot}$ in it go to \ref{b:zzsqrt}. If your function has exponential functions(ex. $3^x$) 
        then go to \ref{b:zzexp}. Otherwise if your function is a ration function meaning the denominator and 
        the numerator are polynomials go to \ref{b:zzrational}.
        \begin{enumerate}[label=(\roman*)]
            \item \label{b:zzsqrt}
                If your function has a square root in it, we will want to multiple the top and bottom by the conjugate. 
                %For example we may have square root part will look something like $\sqrt{g(x)}+ h(x)$ 
                %where $g(x)$ and $h(x)$ are functions. In this case to solve our limit we want to multiply by 
                %$1=\frac{\sqrt{g(x)}- h(x)}{\sqrt{g(x)}- h(x)}$ where $\sqrt{g(x)}- h(x)$ is the conjugate of 
                %$\sqrt{g(x)}+ h(x)$. To simply use the fact that 
                %$(\sqrt{g(x)}+ h(x))(\sqrt{g(x)}- h(x))=g(x)- (h(x))^2$. 
                %This follows from double distribution(which you may have seen called FOIL). 
                Once you simplify try to cancel common terms and continue to \ref{b:step2}.\\
            \item \label{b:zzexp}
                Look up some exponent rules and see if any of them can help you simplify the function so you can cancel common terms.
            \item \label{b:zzrational}
                If your function is a rational function (ex. $f(x)=\frac{3x^5+2x-3}{2x^2-x+1}$), 
                factor the top and bottom, and cancel common terms and continue to step \ref{b:step2}.\\
        \end{enumerate}

        \item\label{b:kz} You found the indeterminate form $\displaystyle{\lim_{x\to c}f(x)}=``\frac{k}{0}''$ 
        for some constant $k$. This indicates that we have a vertical asymptote at $x=c$ and we need to use one sides limits: $\displaystyle{\lim_{x\to c^-}f(x)}$ and $\displaystyle{\lim_{x\to c^+}f(x)}$
        This indeterminate form also indicates that the one sided limits will evaluate to either $\infty$ or $-\infty$. 
        \begin{itemize}
            \item[-] To determine that sign for the $\displaystyle{\lim_{x\to c^-}f(x)}=\pm\infty$. 
            Imagine plugging in a value very close to $x=c$ but to the left (less then $c$), and see what the sign is.\\
            \item[+] To determine that sign for the $\displaystyle{\lim_{x\to c^+}f(x)}=\pm\infty$. 
            Imagine plugging in a value very close to $x=c$ but to the right (greater then $c$), and see what the sign is.
        \end{itemize}
    Do the one sided limits agree? if they don't then the limit does not exist.
    \end{enumerate}
\item \label{b:step2}
Now that you've simplified your limit, try plugging in for $x=c$ again, that is return to step \ref{b:step1}.
    
\end{enumerate}


%\subsubsection{Limits of Piece-wise Functions}
%\label{ssec:pw-number}
% You have determined your function is piece-wise meaning it looks something like 
% $$f(x)=\begin{cases}
%     g_1(x) & \text{ for } x<c\\
%     g_2(x) & \text{ for } x=c\\
%     g_3(x) & \text{ for } x>c\\
% \end{cases}$$
%In this case if we are trying to evaluate the limit as $x$ approaches $c$ (the point where the piece wise function changes) we need to solve the one-side limits: $\displaystyle{\lim_{x\to c^-}f(x)}$ and $\displaystyle{\lim_{x\to c^+}f(x)}$. In this case our goal is to determine if the one-sided limits exist and if they are the same. In this case what ever that value is, is our limit. But if we are trying to evaluate the limit as $x$ approaches some value other then $c$ we can ignore the fact $f(x)$ is piece wise and just look at the corresponding function $g_1(x)$ or $g_3(x)$, depending on where $x$ is approaching(go back to section \ref{ssec:number} looking at the specific function you need).\\

%So if we are looking at the limit as $x$ approaches $c$ we need to solve $\displaystyle{\lim_{x\to c^-}f(x)}$ and $\displaystyle{\lim_{x\to c^+}f(x)}$. So let's look at the negative side first.

%\begin{itemize}
%    \item[-] In this case we will look at the function $g_1(x)$ as this function will give us the outputs for when $x< c$(recall limits never look at the value at $x=c$ so we will ignore the function $g_2$ entirely) Now return to section \ref{ssec:number} to evaluate $\displaystyle{\lim_{x\to c^-}g_1(x)}$.\\
%
%    \item[+] In this case we will look at the function $g_3(x)$ as this function will give us the outputs for when $x> c$(recall limits never look at the value at $x=c$ so we will ignore the function $g_2$ entirely) Now return to section \ref{ssec:number} to evaluate $\displaystyle{\lim_{x\to c^+}g_3(x)}$.\\
%\end{itemize}
%If the limits both exists and are the same then $\displaystyle{\lim_{x\to c}f(x)}$ is that value. Otherwise the limit does not exist.
%


\subsection{Evaluating Limits at Infinity}
\label{ssec:inf}
In this case we are given the limit $\displaystyle{\lim_{x\to \pm\infty}f(x)}$. 

%If $f(x)$ is a piece-wise function we need to treat it differently. Go to section \ref{ssec:pw-inf}.

%Finally if we have $f(x)$ which can be written as a ``normal'' function then we can (probably) follow the steps below to try and evaluate our limit:
\begin{enumerate}
    \item \label{b:infstep1} First try directly plugging in $x=\infty$ or $x=-\infty$ to your function. 
    And simplify, but recall $\infty$ is not a number so we can not simplify 
    $\frac{\infty}{\infty}$ or $\infty-\infty$. Some of the things we can do are: 
    $\infty\cdot\infty=\infty$, $\infty+\infty=\infty$, $k^\infty=\infty$ when $k>1$, 
    $\frac{\infty}{k}=\infty$ when $k\neq 0$, or $k^\infty=0$ when $0<k<1$ and $\frac{k}{\infty}=0$ 
    for any constant $k$. 
    Once you try to plug in for infinity you will get an indeterminate form.
    %one of the following $\frac{k}{\infty}$ for some constant $k$(go to part \ref{b:kinf}), or 
    If you get $\pm\frac{\infty}{\infty}$ go to part \ref{b:infinf}. If you get $\infty-\infty$ go to \ref{b:infminf}.
    If you see something like $\frac{\infty-\infty}{\infty}$ go to \ref{b:infinf} and then \ref{b:infminf}.
    \begin{enumerate}[label=(\alph*)]
        \item \label{b:infinf} You got the indeterminate form 
        $\displaystyle{\lim_{x\to \pm\infty}f(x)}=\frac{\infty}{\infty}$.
        If your function has a $\sqrt{\cdot}$ in it go to \ref{b:2zzsqrt}. If it has an exponential function 
        then go to \ref{b:2zzexp}. Otherwise if your function is a ration function meaning the denominator and the numerator are polynomials go to \ref{b:2zzrational}.\\
        \begin{enumerate}[label=(\roman*)]
            \item \label{b:2zzsqrt} If the denominator is a polynomial go to \ref{b:2zzrational} instead. 
            Otherwise try multiplying by the conjugate on the top and bottom. 
            And then proceed to \ref{b:2zzrational}.\\

            %When working with square roots it is very important to watch out for negatives. 
            %This will likely only come into play when you are evaluating the limit as $x$ goes to $-\infty$. 
            %As a motivating example consider the function $x\sqrt{2x^2}$. 
            %Often it will be easier to work with this function if we bring the outside $x$ into the square root, 
            %and when doing so we need to square it. That is $x\sqrt{2x^2}=\pm\sqrt{x^2}\sqrt{2x^2}=\pm\sqrt{x^2\cdot 2x^2}=\pm\sqrt{2x^4}$. When $x$ is positive or when what we are bringing into the square root is positive we know that the resulting square root is positive($x\sqrt{2x^2}=\sqrt{2x^4}$) However when $x$ is negative or when what we are bringing into the square root is negative then the resulting square root must remain negative ($x\sqrt{2x^2}=-\sqrt{2x^4}$. Notice when $x=-1$ then $x\sqrt{2x^2}=-1\cdot\sqrt{2}=-\sqrt{2}.$ and similarly $-\sqrt{2x^4}=-\sqrt{2}$).\\
            
            \item \label{b:2zzexp} See example \ref{ex:exp2}.\\
            
            \item \label{b:2zzrational} If your function is a rational function (ex. $f(x)=\frac{3x^5+2x-3}{2x^2-x+1}$) 
             then find the term of biggest degree in the bottom (Note: you will need to expand the denominator). This will be the term with the biggest exponent (ex. the biggest degree term of $5x^2+3x^6+x^3$ is $6$ which comes from the $3x^6$ term). 
             Then multiply your function by $1=\frac{\frac{1}{x^n}}{\frac{1}{x^n}}$ where $n$ is the biggest degree you found on the bottom. 
             Simplify the top and bottom of your function and cancel common $x$'s and continue to \ref{b:infstep2}.\\
        \end{enumerate}
        \item \label{b:infminf} If you have $\infty-\infty$ factor your function and continue to \ref{b:infstep2}.
    \end{enumerate}
    \item \label{b:infstep2} Now that you've simplified your limit, try plugging in for $x=\infty$ or $x=-\infty$ again, that is return to step \ref{b:infstep1}.
\end{enumerate}

%\subsubsection{Limits of Piece-wise Functions}
%\label{ssec:pw-inf}
%You have determined your function is piece-wise meaning it looks something like 
% $$f(x)=\begin{cases}
%     g_1(x) & \text{ for } x<b\\
%     g_2(x) & \text{ for } x=b\\
%     g_3(x) & \text{ for } x>b\\
% \end{cases}$$
%for some constant $b$. In this case if we are trying to evaluate the limit as $x$ approaches $\infty$ or $-\infty$ we can ignore the fact $f(x)$ is piece wise and just look at the corresponding function $g_1(x)$ or $g_3(x)$, depending on which side $\infty$ or $-\infty$ is on. That is for
%\begin{itemize}
%    \item[$\infty$] 
%    Return to section \ref{ssec:inf} to evaluate $\displaystyle{\lim_{x\to \infty} g_3(x)}$.\\

%    \item[$-\infty$] 
%    Return to section \ref{ssec:inf} to evaluate $\displaystyle{\lim_{x\to -\infty} g_1(x)}$.\\
%\end{itemize}

\subsection{Examples}
\label{ssec:examples}
\subsubsection{Example 1}
\label{ex:abs}
For $g(x)=\frac{|x-2|}{x-2}$, find $\displaystyle{\lim_{x\to 2}g(x)}$, $\displaystyle{\lim_{x\to 2^{-}}g(x)}$ and $\displaystyle{\lim_{x\to 2^{+}}g(x)}$.\\ 
First lets determine if this function has any points that are discontinuous. Notice that the denominator is $x-2$ and when $x=2$ the denominator is $2-2=0$. So we know that $g(x)$ is not defined when $x=2$.\\

Now when ever we are working with absolute values we want to rewrite our function as a piece wise function. Recall that for the function $f(x)=|x|$ we can rewrite it as 
$$f(x)=|x|=\begin{cases}
        x & \text{for } x < 1\\
        -x & \text{for } x \geq 1  
    \end{cases}$$
So when $x$ is positive the absolute values does nothing and when the function is negative we add another negative, making it $-x$, canceling out the negative in the input.\\

Now if we wanted to rewrite the function $g(x)$ as a piece wise function, we need to first determine when the function inside the absolute value is negative and when its positive. Looking at our function we can see that $x-2$ is negative when $x<2$ and similarly we know that $x-2$ is positive when $x>2$. So we will split our function onto two functions at the point $x=2$(And because $x=2$ is not defined we will not include this point). First when $x> 2$ or when $x-2$ is positive we know that our function is $\frac{|x-2|}{x-2}=\frac{x-2}{x-2}=1$, which we can cancel as $x>2$ and therefore $x\neq 2$. And when $x<2$ we know that $|x-2|= -(x-2)$, so our function is $\frac{|x-2|}{x-2}=\frac{-(x-2)}{x-2}=-1$, which we can cancel our as $x<2$ and therefore not equal to $2$. This gives us the piece wise function 
$$g(x)=\frac{|x-2|}{x-2}=\begin{cases}
        -1 & \text{for } x < 2\\
        1 & \text{for } x > 2  
    \end{cases}$$
which is defined for all $x$ except $x=2$. So now lets look at the one sided limits of $g(x)$. First lets look at what happens as $x$ approached $2$ from the negative side, where we see that $\displaystyle{\lim_{x\to 2^{-}}g(x)}=\displaystyle{\lim_{x\to 2^{-}}-1}=-1$, and similarly for $x$ approaches $2$ from the positive side we get that $\displaystyle{\lim_{x\to 2^{+}}g(x)}=\displaystyle{\lim_{x\to 2^{+}}1}=1$. Now because the one sided limits not not agree we can conclude that the limit $\displaystyle{\lim_{x\to 2}g(x)}$ Does not exist.



\subsubsection{Example 2}
\label{ex:exp2}

Consider the function $f(x)=\frac{2^{x}-2}{4^{x}-1}$. Notice that if we try to directly substitute $\displaystyle{\lim_{x\to\infty}\frac{2^{x}-2}{4^{x}-1}}=\frac{\infty}{\infty}$. So we must simplify.\\

To do this we will multiply by $4^{-x}$ on the top and bottom and simplify. This give us
$$\displaystyle{\lim_{x\to\infty}\frac{2^{x}-2}{4^{x}-1}}\frac{4^{-x}}{4^{-x}}=\lim_{x\to\infty}\frac{2^{x}4^{-x}-2\cdot4^{-x}}{4^{x}4^{-x}-4^{-x}}=\lim_{x\to\infty}\frac{2^{x}\left(2^{-x}\right)^{2}-2\cdot\left(2^{-x}\right)^{2}}{4^{x}4^{-x}-4^{-x}}=\lim_{x\to\infty}\frac{2^{-x}-2\cdot2^{-2x}}{1-4^{-x}}$$
Notice that at this point we can directly substitute and get
$\displaystyle{\lim_{x\to\infty}\frac{\left(2^{x}-2\right)}{4^{x}-1}}=\lim_{x\to\infty}\frac{2^{-x}-2\cdot2^{-2x}}{1-4^{-x}}=\frac{0-0}{1}=0$.\\




\end{document}
