\documentclass[12pt]{report}

\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\setlength\parindent{0pt}

\usepackage{graphicx, amsmath,anonchap,tabularx, multicol,verbatim}

\usepackage{enumitem}
\setlist{noitemsep}
\setlist{nolistsep}

\begin{document}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l l}
\textbf{The Algebra of Limits- Factoring and Conjugates}  & Jedi Name: \hrulefill \\
MATH 160 Section That's No Moon! &  Side?: \rule{6cm}{0.5pt}\\
\hline\hline
\end{tabular*} \\

\pagenumbering{gobble}

\sf
Learning Targets:
\begin{itemize}
\item Identify when a limit cannot be computed via direct substitution. 
\item Evaluate limits of indeterminate form 0/0 algebraically using factoring.
\item Evaluate limits of indeterminate form 0/0 algebraically using multiplication by the conjugate
\end{itemize}

Aligns with Standard S2 (Indeterminate Limits), adjacent to Standard L2 (Limit Evaluation).
\rm

\hrulefill

\begin{enumerate}
\item Limits!  Evaluate the following limits using algebra. Try plug and chug, but if that doesn't work, try  factoring and then canceling a factor to get rid of the division by zero issue. Pay attention to limit notation and how you use ``=''.

\vspace{1cm}

\begin{multicols}{2}
\begin{enumerate}

\item $\displaystyle\lim_{t\rightarrow -3}\frac{t^2+6t+9}{t+3}$
\vskip 4cm

\item $\displaystyle\lim_{x\rightarrow -3}\frac{x+3}{x^2-9}$
\vskip 4cm
%
%\item $\displaystyle\lim_{x\rightarrow4}\frac{x^2-16}{x-4}$
%\vskip 4cm

\item $\displaystyle\lim_{t\rightarrow-2}\frac{t^2-5t-14}{t^2-4}$
\vskip 4cm

\item $\displaystyle\lim_{s\rightarrow100}\frac{100-s}{10-\sqrt{s}}$
\vskip 4cm

%\item $\displaystyle\lim_{t\rightarrow-3}\frac{t-3}{t^2-9}$

%\vskip 4cm

\end{enumerate}
\end{multicols}



\vskip 4cm
\item More Limits!  Evaluate the following limits using algebra. Try plug and chug, but if that doesn't work, try multiplying by the conjugate and then canceling a factor to get rid of the division by zero issue.  Pay attention to limit notation and how you use ``=''.

\vspace{1cm}


\begin{enumerate}

\item $\displaystyle\lim_{x\rightarrow 6}\frac{4-\sqrt{3x-2}}{6-x}$
\vskip 4cm

\item $\displaystyle\lim_{y\rightarrow4}\frac{4-y}{5-\sqrt{y^2+9}}$
\vskip 4cm

%\item $\displaystyle\lim_{s\rightarrow100}\frac{100-s}{10-\sqrt{s}}$
%\vfill

%\item $\displaystyle\lim_{y\rightarrow 36}\frac{36-y}{6-\sqrt{y}}$
%\vfill

\item $\displaystyle\lim_{x \to 8}\frac{|x-8|}{x-8}$
\vskip 4cm

\item $\displaystyle\lim_{x \to 7}\frac{(x-7)^2}{|x-7|}$
\vskip 4cm

\end{enumerate}	

\item Determine whether the following statement is true or false. If it is true, explain why.  If it is false, give a counter-example. \\

\begin{center}
If $\displaystyle{\lim_{x\to 5}} f(x) = 0$ and $\displaystyle{\lim_{x\to 5}} g(x) = 0$, then $\displaystyle{\lim_{x\to 5}} \frac{f(x)}{g(x)}$ does not exist. 
\end{center}


\end{enumerate}

\end{document}
